A primer to numerical simulations: The perihelion motion of Mercury

### 2018-01-15 tex/MercuryNumerical.tex
code style bugfix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{The complete code}\label{sec:code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Below we provide the complete code as developed above.
\lstinputlisting[language=Python,basicstyle=\scriptsize]{mercury_orbit_base.py}
Further examples and template files can be found online \cite{scripts}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{The complete code}\label{sec:code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Below we provide the complete code as developed above.
\lstinputlisting[language=Python,basicstyle=\linespread{1}\scriptsize\ttfamily]{mercury_orbit_base.py}
Further examples and template files can be found online \cite{scripts}.
